ms_tables

### 2017-12-18 man/ms_tables.Rmd
update tables

colnames(dff) <- c("", "rc\nF", "rc\np", "rrs\nF", "rc\np", "rs\nF", "rc\np", "rt\nF", "rc\np")
pander(dff,
             round=c(0,2,3,2,3,2,3,2,3),
             digits=c(0,5,4,5,4,5,4,5,4),
             keep.line.breaks = TRUE
             )
dff

@@

>>>>

colnames(dff) <- c("", "rc\nF", "rc\np", "rrs\nF", "rrs\np", "rs\nF", "rs\np", "rt\nF", "rt\np")
pander(dff,
             round=c(0,2,3,2,3,2,3,2,3),
             digits=c(0,5,4,5,4,5,4,5,4),
             keep.line.breaks = TRUE
             )
dff

@@

### Table R4 sin rrs

dff <- df %>% 
  filter(variables != "rrs") %>% 
  gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Disturb", 
                           "disturb_year:site" = "Disturb X Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Disturb", "Site", "Disturb X Site")))

colnames(dff) <- c("", "rc\nF", "rc\np", "rs\nF", "rs\np", "rt\nF", "rt\np")
pander(dff,
             round=c(0,2,3,2,3,2,3,2,3),
             digits=c(0,5,4,5,4,5,4,5,4),
             keep.line.breaks = TRUE
             )
dff
